### 2019-11-08 thesis/txt/0-introduction.tex
small corrections before sending to annibale

CI builds produce long and verbose build logs~\cite{beller2017oops}, reporting the progress and results of the steps within the build.
The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
Build logs are a valuable data source: For developers, who read them to analyze why their build failed or how different stages of the build process perform.
Second, for researchers, who can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.

@@

These approaches have various downsides and strengths:
Regular expressions are very exact but difficult to maintain~\cite{michael2019regexes}.
Custom parsers are powerful though fragile towards changes in the log structure.
Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
Developers and researches currently have little support while choosing which technique to use for a retrieval task.

The goal of this thesis is to investigate different chunk retrieval techniques (CR techniques) for build logs and describe under which circumstances we recommend each of the techniques.
We aim to define a model to characterize different CR techniques, as well as the information retrievable from CI build logs.
For \textbf{RQ1}, we analyze which criteria influence the suitability of an CR technique for CI build logs.
We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as CTS) and
  \item keyword search (referred to as KWS)
\end{itemize}
\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
how many examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the configuring examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
% \begin{simplebox}{Research Questions}
% \begin{itemize}
%   \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
%   \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
%   \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
%   \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
% \end{itemize}
% \end{simplebox}
To evaluate PBE, CTS and KWS we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.

Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that
\begin{itemize}
  \item PBE yields very accurate results when configured with 1 to 3 examples from a single structural category.
  \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
  A small increase in the number of examples used in the configuration has no visible influence and fewer structural categories improve the retrieval accuracy.
  \item KWS has the highest recall of all techniques combined with considerable lower recall.
  It is the only technique where retrieval quality does not decrease with and increasing number of structural categories in the configuring examples.
\end{itemize}
We recommend PBE for use cases where the desired information is always represented in the same structurally predictable way and a high confidence in the exactness of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
In cases where the representation fo the desired information is unpredictable or varies greatly, KWS is the best technique to choose.
Though the low precision of the output requires a human to interpret the output of the chunk retrieval.

@@

This thesis first presents an overview of related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
Next, chapter~\ref{sec:models} characterizes chunk retrieval techniques and contained and retrievable information from CI build logs.
It also introduces the three investigated techniques PBE, CTS and KWS.
Chapter~\ref{sec:data-set} describes the creation of the \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs, including the labeling and the validation process.
Following, Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter~\ref{sec:study}.
Chapter~\ref{sec:discussion} presents the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.
\end{document}

>>>>

CI builds produce long and verbose build logs~\cite{beller2017oops}, reporting the progress and results of the steps within the build.
The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
Build logs are a valuable data source: For developers, who read them to analyze why their build failed or how different stages of the build process perform.
Second, for researchers, who can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
However, these two groups can only use the information within the build logs if they can adequately retrieve the information relevant to them.

@@

These approaches have various downsides and strengths:
Regular expressions are exact but difficult to maintain~\cite{michael2019regexes}.
Custom parsers are powerful though fragile towards changes in the log structure.
Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
Developers and researches currently have little support while choosing which technique to use for a retrieval task.

The goal of this thesis is to investigate different chunk retrieval techniques (CR techniques) for build logs and describe under which circumstances we recommend each of the techniques.
We aim to define a model to characterize different CR techniques, as well as the information retrievable from CI build logs.
For \textbf{RQ1}, we analyze which criteria influence the suitability of a CR technique for CI build logs.
We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as CTS) and
  \item keyword search (referred to as KWS)
\end{itemize}
\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
how many examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the configuring examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
% \begin{simplebox}{Research Questions}
% \begin{itemize}
%   \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
%   \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
%   \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
%   \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
% \end{itemize}
% \end{simplebox}
To evaluate PBE, CTS and KWS we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.

Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that
\begin{itemize}
  \item PBE yields very accurate results when configured with 1 to 3 examples from a single structural category.
  \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
  A small increase in the number of examples used in the configuration has no visible influence and fewer structural categories improve the retrieval accuracy.
  \item KWS has the highest recall of all techniques combined with much lower recall.
  It is the only technique where retrieval quality does not decrease with an increasing number of structural categories in the configuring examples.
\end{itemize}
We recommend PBE for use cases where the desired information is always represented in the same structurally predictable way and high confidence in the exactness of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
In cases where the representation fo the desired information is unpredictable or varies greatly, KWS is the best technique to choose.
Though the low precision of the output requires a human to interpret the output of the chunk retrieval.

@@

This thesis first presents an overview of related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
Next, chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and contained and retrievable information from CI build logs.
It also introduces the three investigated techniques PBE, CTS and KWS\@.
Chapter~\ref{sec:data-set} describes the creation of the \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs, including the labeling and the validation process.
Following, Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter~\ref{sec:study}.
Chapter~\ref{sec:discussion} presents the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.
\end{document}
